Ejemplificando art

### 2023-11-02 notebooks/example_script.Rmd
Discards writing canonical markdown to avoid wrapping lines

---
title: "Ejemplificando art"
author: "Mario Luzardo"
date: "2023-07-13"
output:
  word_document:
    fig_width:  6
    fig_height: 6
editor_options:
  markdown:
    canonical: true
---

>>>>

---
title: "Ejemplificando art"
author: "Mario Luzardo"
date: "2023-07-13"
output:
  word_document:
    fig_width:  6
    fig_height: 6
editor_options:
  markdown:
    canonical: false
---
